Air cargo load and route planning in pickup and delivery operations

### 2024-01-26 latex/eswa.tex
GA TSP solver included

@@

	For these tests, we considered the odd instances (1, 3, 5, 7) as the \textbf{training} set and the even instances (2, 4, 6) as the \textbf{testing} set for the \textit{iRace} runs. We supplied \textit{iRace} for $threshold_1$ determination, the range [0.8, 1.0], and for $threshold_2$, the range [1.0, 2.0]. The number of iterations in each experiment was limited to 3000 executions for \textit{iRace} to have plenty of data for its statistical tests. More detail about these configurations may be found on the \textit{iRace} user guide in {\tt cran.r-project.org/web/packages/irace/irace.pdf}.

@@

@@

Table \ref{tab:100time} shows the results obtained with the strategy of testing the $K!$\/ tours in all scenarios with different $tmax$. We can observe more cases where $Gurobi$\/ fails, even in smaller scenarios. When $Gurobi$\/ finishes, $Shims$\/ finds a solution of similar quality ($98\%$\/ or better). In all cases, $Shims$\/ finds a good solution in less than 4 minutes.

@@

		\multirow{10}{*}{$Gurobi$} & \multirow{2}{*}{240s} & $f$ & 8.53 & 12.24 & 13.34 &  x      &  x      & 11.81 & 17.02 & 18.31 &  x      &  x      & 17.75 & 25.24 & x     & x       & x \\ 
		&               &  {time (s)}                              & 41   & 43    & 123   &  x      &  x      & 50    & 62    & 181   &  x      &  x      & 166   & 140   & x     & x       & x \\ 
		\cmidrule(lr){2-18}

		&                              \multirow{2}{*}{1200s} & $f$ & 8.52 & 12.25 & 13.31 & 14.67   & x       & 11.81 & 17.02 & 18.25 &  20.64  &  x      & 17.75 & 25.24 & 26.49 & 27.97   & x \\ 
		&        &  {time (s)}                             & 39   & 41    & 129   & 217     & x       & 52    & 61    & 190   &  304    &  x      & 161   & 139   & 384   & 579     & x \\ 
		\cmidrule(lr){2-18}                              
		& \multirow{2}{*}{2400s}& $f$                               & 8.53 & 12.25 & 13.30 & 14.59   & 13.59   & 11.80 & 17.02 & 18.25 &  20.60  &  x      & 17.75 & 25.24 & 26.46 & 29.10   & x \\
		&        &  {time (s)}                             & 33   & 39    & 127   & 313     & 1444    & 51    & 62    & 188   &  327    &  x      & 158   & 127   & 381   & 543     & x \\
		\cmidrule(lr){2-18}

		& \multirow{2}{*}{3600s}& $f$                               & 8.52 & 12.25 & 13.32 & 14.61   & x       & 11.81 & 17.01 & 18.25 &  20.59  & 18.36   & 17.75 & 25.24 & 26.46 & 29.11   & x \\ 
		&        &  {time (s)}                             & 25   & 36    & 121   & 297     & x       & 53    & 61    & 193   &  470    & 2241    & 151   & 123   & 319   & 689     & x \\

@@

		\multirow{2}{*}{$Shims$} & \multirow{2}{*}{240s}  & $f$ & 8.54 & 12.26 & 13.23 & 14.53   & 13.42   & 11.83 & 17.00 & 18.21 &  20.45  & 18.00   & 17.78 & 25.25 & 26.38 & 28.98   & 26.08 \\ % 
		&         & {time (s)}                             & 1    & 2     & 6     & 17      & 109     & 1     & 2     & 8     &  26     & 160     & 2     & 3     & 13    & 37      & 229   \\

@@

>>>>

{\color{blue}

As for the size of the problem dealt with in this work, addressing the scale of the Travelling Salesperson Problem (TSP) in practical, real-world air transport contexts indeed reveals a fascinating and complex challenge. In the realm of academic research, TSP problems often explore theoretical models that can scale to hundreds or even larger numbers of cities.

In practical terms, especially within the air transport sector, the size and complexity of a TSP can vary significantly depending on several factors:

\textbf{Fleet and Route Planning}: For airline operations, the problem isn't just about finding the shortest path through a set of points but also involves scheduling, aircraft assignment, crew scheduling, and maintenance planning. This multi-dimensional complexity transforms a standard TSP into a more intricate problem in our study, the Pickup and Delivery Problem (PDP).

\textbf{Operational Constraints}: Factors like weather, air traffic control restrictions, and the availability of take-off and landing slots make real-world TSP scenarios in air transport even more challenging. These constraints add layers of complexity that significantly depart from the theoretical TSP model.

\textbf{Dynamic Nature}: Unlike the static nature of classical TSP, real-world problems in air transport are highly dynamic. Routes need to be optimized continuously as conditions change, requiring algorithms that can adapt in real-time or near-real-time.

In practical air transport scenarios, the size of a TSP can therefore be less about the sheer number of nodes and more about the complexity and dynamic nature of the problem, which in our case (a single aircraft in a single day) is rarely expected to be more than seven nodes, based on the experience of the first author when working on an operations control centre.
}

@@

	For these tests, we considered the odd instances (1, 3, 5, 7) as the \textbf{training} set and the even instances (2, 4, 6) as the \textbf{testing} set for the \textit{iRace} runs. We supplied \textit{iRace} for $threshold_1$ determination, the range [0.8, 1.0], and for $threshold_2$, the range [1.0, 2.0]. The number of iterations in each experiment was limited to 3000 executions for \textit{iRace} to have plenty of data for its statistical tests. More detail about these configurations may be found on the \textit{iRace} user guide in {\tt cran.r-project.org/web/packages/irace/irace.pdf}.
}

@@

\begin{table}[H]
{\color{blue}
	\centering
	\caption{Overall results}  \label{tab:mr}
	\footnotesize
	\begin{tabular}{cccc}	
	\toprule
	{\bf Method} & {\bf Best scenarios} & {\bf Worst scenarios} & {\bf Worst run times (min)}  \\
	\midrule
	NMO           & 4             & 5    & {\color{red}60}  \\
	ACO           & 2, 3          & 4, 5 & {\color{red}25}, {\color{red}61}  \\
	GRASP         & 1             & 4, 5 & {\color{red}28}, {\color{red}55}  \\
	TS            & -             & 5    & {\color{red}44}  \\
	\midrule
	{\it Gurobi}  & 1, 2, 3, 4    & 5    & {\color{red}did not solve}  \\
	{\it Shims}   & 1, 2, 3, 4, 5 & -    & {\bf 3.26} \\
	\bottomrule
	\end{tabular}
\normalsize
}
\end{table}

\subsubsection{Shims results}

@@

Table \ref{tab:100time} shows the results obtained with the strategy of testing the $K!$\/ tours in all scenarios with different $tmax$. We can observe more cases where $Gurobi$\/ fails, even in smaller scenarios. When $Gurobi$\/ finishes, $Shims$\/ finds a solution of similar quality ($99\%$\/ or better). In all cases, $Shims$\/ finds a good solution in less than 4 minutes.

@@

		\multirow{10}{*}{$Gurobi$} & \multirow{2}{*}{240s} & $f$ & 8.53 & 12.24 & 13.34 &  {\bf x}& {\bf x} & 11.81 & 17.02 & 18.31 & {\bf x} & {\bf x} & 17.75 & 25.24 & {\bf x} & {\bf x} & {\bf x} \\ 
		&               &  {time (s)}                            & 41   & 43    & 123   &  {\bf x}& {\bf x} & 50    & 62    & 181   & {\bf x} & {\bf x} & 166   & 140   & {\bf x} & {\bf x} & {\bf x} \\ 
		\cmidrule(lr){2-18}

		&                           \multirow{2}{*}{1200s} & $f$ & 8.52 & 12.25 & 13.31 & 14.67   & {\bf x} & 11.81 & 17.02 & 18.25 &  20.64  & {\bf x} & 17.75 & 25.24 & 26.49 & 27.97   & {\bf x} \\ 
		&        &  {time (s)}                                   & 39   & 41    & 129   & 217     & {\bf x} & 52    & 61    & 190   &  304    & {\bf x} & 161   & 139   & 384   & 579     & {\bf x} \\ 
		\cmidrule(lr){2-18}                              
		&                           \multirow{2}{*}{2400s} & $f$ & 8.60 & 12.21 & 13.67 & 15.00   & 13.41   & 11.77 & 16.38 & 18.02 & 20.94   & {\bf x} & 17.75 & 25.24 & 26.46 & 29.10   & {\bf x} \\
		&        &  {time (s)}                                   & 26   & 38    & 134   & 310     & 1520    & 46    & 60    & 206   & 474     & {\bf x} & 158   & 127   & 381   & 543     & {\bf x} \\
		\cmidrule(lr){2-18}

		&                           \multirow{2}{*}{3600s} & $f$ & 8.60 & 12.20 & 13.66 & 15.00   & {\bf x} & 11.76 & 16.37 & 18.01 &  20.95  & 17.60   & 17.90 & 25.44 & 26.15 & 29.13   & {\bf x} \\ 
		&        &  {time (s)}                                   & 30   & 35    & 123   & 314     & {\bf x} & 64    & 58    & 195   &  472    & 2258    & 178   & 143   & 378   & 862     & {\bf x} \\

@@

		\multirow{2}{*}{$Shims$} &  \multirow{2}{*}{240s}  & $f$ & 8.61 & 12.20 & 13.46 & 14.99   & 13.35   & 11.78 & 16.29 & 17.99 &  20.93  & 17.50   & 17.94 & 25.45 & 26.14 & 28.84   & 26.22 \\ % 
		&         & {time (s)}                                   & 1    & 2     & 4     & 10      & 51      & 1     & 2     & 5     &  15     & 100     & 1     & 3     & 10    & 31      & 196   \\

@@

{\color{blue}
\subsection{{\it Shims} validation with more nodes}

To validate the effectiveness of the {\it Shims} heuristic, we solve a 15-node TSP containing the 15 main Brazilian airports.
For this task, we implemented a TSP solution method based on the Genetic Algorithm (GA) that returns the 20\% best tours as input to the ACLP-RPDP solved by {\it Shims}.
